Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-03-18 jss/EpiCompare-paper/EpiCompare-paper.Rmd
Small edits in paper writing for Ben

In this section, we present the tools implemented in \pkg{EpiCompare} and explain how they aid in the  data analysis pipeline.  In Fig. \ref{fig:pipeline2}, we illustrate how our \ben{\sout{package fits} package's functions fit} into the data analysis pipeline introduced in Fig. \ref{fig:pipeline}.  All front-facing functions are aimed to be as user-friendly as possible, and we focus on providing the user "tidyverse" style functions, that encourage piping and also follow clear verb naming schemes \citep{Wickham2019}. Although users can typically incorporate \pkg{EpiCompare} into any step in the data analysis process, there are two primary points of entry.  The first point of entry is the very beginning with pre-processing and visualizing raw data, and the second point of entry is after modeling and simulation. Figure \ref{fig:pipeline2} captures these different paths, and we will highlight both approaches and how to leverage \pkg{EpiCompare} in the subsections below.

@@

The first step of most data analysis is cleaning up the data \ben{so it can \sout{to}} be explored. There are multiple ways to collect the epidemiological data. Sometimes individual records \ben{are collected}, with times of different states of the epidemic (infection, recovery, etc.) as well as individual information like network structure, location, and sub-population information\ben{.\sout{will be collected, whereas}} \ben{O}ther data collections will focus on aggregate counts of individuals in each epidemic state.  In fact, usually only the number of new infections at each time step is observed and the compartment totals \ben{(amounts of individuals in each state)} are then imputed from that along with other information about the disease and the population of interest.  \ben{In \pkg{EpiCompare}, w}e focus on understanding the overall impact of an outbreak at the aggregate/population level, \ben{which allows examination of overall trends of an epidemic more easily}.

@@

\ben{[Ben says: this whole paragraph is new]} In order to help the practitioner to a point in which they can examine their epidemics from an aggregate/ population lens, we provide a function called `agents_to_aggregate`. This function transforms data that contains information about individual/agents' initial entry into each state (e.g. start of infection, start of recovery, etc) to an aggregate view of how many individuals where in a state at a given time. There are often situations where grouping agents into subpopulations (e.g. subpopulations defined by age or sex) can highlight different aggregate level trends. Papers like \citet{rvachev1985,anderson1992,worby2015} also develop state-based models that account for subpopulations in their models\footnote{\ben{[Ben says: I don't really like this sentence, but I'm trying to include the references - are they needed?]}}. This function allows the user to easily group agents into new subpopulations by using the \pkg{tidyverse} paradigm to first `group_by()`^[The `group_by` function is from the \pkg{dplyr} package.] the subpopulation defining features and then aggregate (using `agents_to_aggregate`) conditional on these subpopulations.

\ben{[Ben says: this whole paragraph is new]} The `agents_to_aggregate` function is also flexible to deal with a wide range of information about each individual. It can account for infinitely many states, allowing the practioner to aggregate information relative to the standard "Suspectible", "Infectious", and "Recovered" states (CITE) or also add states like "Exposed", "iMmune", "Hospitalized" and more. Additionally, `agents_to_aggregate` also permits indicators for death/exit and birth/entry dates (that change the overall number of individuals in the population). This function is the highest tested function in this package, and can deal with many nuances that might come-about in the individual data. For these reasons, we view `agents_to_aggregate()` as powerful tool in the step of pre-processing data, one that quickly and simply transforms individual level information into an aggregate view that can be processed and analyzed in a simpler manner.

@@

\ben{[Ben says: this is actually an older version:]} With raw data, getting to know our data now-a-days very frequently means figuring out good combinations of visualizations, numerical summaries and subsetting. An expert coder can start from `agents_to_aggregate` to successfully do this in many ways, but we’ve also developed tools to rapidly explore your data if your have a 3 unique states models (like the SIR model). Our `geom_aggregate` provides a rapid way to explore different subpopulations experience of the epidemic, and combines the ideas behind agents_to_aggregate for the SIR case, with `geom_path` and `coord_term` to visualize any number of groups epidemic trajectory in 3d simplex space using `ggplot2` and `ggtern` \citep{Wickham2016, Hamilton2018}. Visualization tools for SIR models were developed because (1) SIR models are some of the most common and basic epidemic state-based models and (2) our simplex representation of these epidemics emphasizes a "time-invarance" representation of the data (for a refresher see Section \ref{sec:time-invariant}).

@@

Although this package does not focus on estimating a model for the data, we do provide some flexible functions for simulation of basic discrete-time epidemic-state models with Bernoulli/Multinomial transitions which can be used to (noisily) approximate ODEs which describe transitions from one state to the next^[The original sentence seemed clearer to me (it may even be a run-on sentence now). I'm wondering if you didn't like the original sentence relative to the "truth-ful-ness" of the statement? Here's the original sentence slightly edited: "Although this package does not focus on estimating a model for the data, we do provide some power functions for simulation of basic state models with Bernoulli approximation of ODE state models encoded in simulate_agents and simulate_SIR_agents".].  These functions can be naturally combined with `agents_to_aggregate()` to proceed in the pipeline.  The function `simulate_SIR_agents()` simulates an SIR epidemic with user inputs for the number of simulations, the initial number in each state, the infection and recovery parameters $(\beta, \gamma$), and the total number of discrete time steps.  This function allows for easy access to SIR model analysis and comparison.  Beyond SIR models, the function `simulate_agents()` takes as input a user-specified transition matrix and other epidemic parameters to allow the user to create simulations of an outbreak for \textit{any} number of states and any number of transitions among them.  This allows for users to explore the space of models in an intuitive way without getting bogged down by too much mathematical detail. For consistency, we have made output from `simulate_agents()` and `simulate_SIR_agents()` compatible with `agents_to_aggregate()` so aggregate information may easily be accessed.

@@

Post-processing of modeling and simulation consists of making summary statistics, plots, tables, and other ways to disseminate information to the public.  For example, comma separated value files (`.csv`) are a  standard way to share information within tables.  However, model output is often far more complicated than what a traditional `.csv` would allow.  As a result, a number of epidemic modeling packages return a special class, specific to their modeling.  The special classes often contain a plethora of information from residuals, model diagnostics, input parameters, and more.  While incredibly useful, these special classes can be difficult for novice coders to navigate.

>>>>

In this section, we present the tools implemented in \pkg{EpiCompare} and explain how they aid in the  data analysis pipeline.  In Fig. \ref{fig:pipeline2}, we illustrate how our \ben{\sout{package fits} package's functions fit} into the data analysis pipeline introduced in Fig. \ref{fig:pipeline}.  All front-facing functions are aimed to be as user-friendly as possible. We also focus on providing the user "tidyverse" style functions, that encourage piping and also follow clear verb naming schemes \citep{Wickham2019}. Although users can typically incorporate \pkg{EpiCompare} into any step in the data analysis process, there are two primary points of entry.  The first point of entry is the very beginning with pre-processing and visualizing raw data, and the second point of entry is after modeling and simulation. Figure \ref{fig:pipeline2} captures these different paths, and we will highlight both approaches and how to leverage \pkg{EpiCompare} in the subsections below.

@@

The first step of most data analysis is cleaning the data \ben{so it can \sout{to}} be explored. There are multiple ways to collect epidemiological data. Sometimes individual records \ben{are collected}, with times of different states of the epidemic (infection, recovery, etc.) as well as individual information like network structure, location, and sub-population information\ben{.\sout{will be collected, whereas}} \ben{O}ther data collections focus on aggregate counts of individuals in each epidemic state.  In fact, usually only the number of new infections at each time step (e.g. weekly case counts) is observed.  Compartment totals \ben{(amounts of individuals in each state)} are then imputed from those case counts along with other information about the disease and the population of interest.  \ben{In \pkg{EpiCompare}, w}e focus on understanding the overall impact of an outbreak at the aggregate/population level, \ben{which allows examination of overall trends of an epidemic more easily}.

@@

\ben{[Ben says: this whole paragraph is new]} In order to help the practitioner examine epidemics from an aggregate/ population lens, we provide a function called `agents_to_aggregate`. This function transforms data about individual/agents' initial entry into each state (e.g. start of infection, start of recovery, etc) to an aggregate view of how many individuals where in a state at a given time. There are often situations where grouping agents into subpopulations (e.g. subpopulations defined by age or sex) can highlight different aggregate level trends. For example, research by \citet{rvachev1985,anderson1992,worby2015} develop state-based models that account for subpopulations in their models\footnote{\ben{[Ben says: I don't really like this sentence, but I'm trying to include the references - are they needed?]}}. This function allows the user to easily group agents into new subpopulations by using the \pkg{tidyverse} paradigm to first `group_by()`^[The `group_by` function is from the \pkg{dplyr} package.] the subpopulation defining features and then aggregate (using `agents_to_aggregate`) conditional on these subpopulations.  \shannon{I think these last two sentences are repetitive}

\ben{[Ben says: this whole paragraph is new]} The `agents_to_aggregate` function is also flexible to deal with a wide range of information about each individual. It can, theoretically, account for infinitely many states, allowing the practitioner to aggregate information relative to the standard "Suspectible", "Infectious", and "Recovered" states (CITE) or also add states like "Exposed", "iMmune", "Hospitalized" and more. Additionally, `agents_to_aggregate` also permits indicators for death/exit and birth/entry dates (that change the overall population size). \shannon{Don't think this is necessary \sout{This function is the highest tested function in this package, and can deal with many nuances that might come-about in the individual data.}} The function `agents_to_aggregate()` is a powerful tool in the step of pre-processing data, one that quickly and simply transforms individual level information into an aggregate view that can be processed and analyzed in a simpler manner.

@@

\ben{[Ben says: this is actually an older version:]} With raw data, "getting to know" our data currently means figuring out good combinations of visualizations, numerical summaries and subsets. An expert coder can start from `agents_to_aggregate` to successfully do this in many ways, but \pkg{EpiCompare} also includes tools to rapidly explore your data if your has at least three epidemic states (although these tools work best with exactly three epidemic states). Our `geom_aggregate` provides a rapid way to explore different subpopulations' experience of the epidemic, and combines the ideas behind `agents_to_aggregate` for the SIR case, with `geom_path` and `coord_tern` to visualize any number of groups epidemic trajectory in 3d simplex space using \pkg{ggplot2} and \pkg{ggtern} \citep{Wickham2016, Hamilton2018}. Visualization tools for SIR models were developed because (1) SIR models are some of the most common and basic epidemic state-based models and (2) our simplex representation of these epidemics emphasizes a "time-invarance" representation of the data (for a refresher see Section \ref{sec:time-invariant}).

@@

Although this package does not focus on fitting a model to data, we do provide some flexible functions for simulation of basic discrete-time epidemic-state models.\sout{ with Bernoulli or Multinomial transitions which can be used to (noisily) approximate ODEs which describe transitions from one state to the next}^[The original sentence seemed clearer to me (it may even be a run-on sentence now). I'm wondering if you didn't like the original sentence relative to the "truth-ful-ness" of the statement? Here's the original sentence slightly edited: "Although this package does not focus on estimating a model for the data, we do provide some power functions for simulation of basic state models with Bernoulli approximation of ODE state models encoded in simulate_agents and simulate_SIR_agents".].  These functions can be naturally combined with `agents_to_aggregate()` to proceed in the pipeline.  The function `simulate_SIR_agents()` simulates an SIR epidemic with user inputs for the number of simulations, the initial number in each state, the infection and recovery parameters $(\beta, \gamma$), and the total number of discrete time steps.  This function allows for easy access to SIR model analysis and comparison.  Beyond SIR models, the function `simulate_agents()` takes as input a user-specified transition matrix and other epidemic parameters to allow the user to create simulations of an outbreak for \textit{any} number of states and any number of transitions among them.  This allows for users to explore the space of models in an intuitive way without getting bogged down by too much mathematical detail. For consistency, we have made output from `simulate_agents()` and `simulate_SIR_agents()` compatible with `agents_to_aggregate()` so aggregate information may easily be accessed.

@@

Post-processing of modeling and simulation consists of making summary statistics, plots, tables, and other ways to disseminate information to the public.  For example, comma separated value files (`.csv`) are a  standard way to share information within tables.  However, model output is often far more complicated than what a traditional `.csv` would allow.  \shannon{Do we need three sentences about csvs?} As a result, a number of epidemic modeling packages return a special class, specific to their modeling.  The special classes often contain a plethora of information from residuals, model diagnostics, input parameters, and more.  While incredibly useful, these special classes can be difficult for novice coders to navigate.

### 2021-03-18 jss/EpiCompare-paper/EpiCompare-paper.tex
Small edits in paper writing for Ben

In this section, we present the tools implemented in \pkg{EpiCompare}
and explain how they aid in the data analysis pipeline. In Fig.
\ref{fig:pipeline2}, we illustrate how our
\textcolor{violet}{\sout{package fits} package's functions fit} into the
data analysis pipeline introduced in Fig. \ref{fig:pipeline}. All
front-facing functions are aimed to be as user-friendly as possible, and
we focus on providing the user ``tidyverse'' style functions, that
encourage piping and also follow clear verb naming schemes
\citep{Wickham2019}. Although users can typically incorporate
\pkg{EpiCompare} into any step in the data analysis process, there are
two primary points of entry. The first point of entry is the very
beginning with pre-processing and visualizing raw data, and the second
point of entry is after modeling and simulation. Figure
\ref{fig:pipeline2} captures these different paths, and we will
highlight both approaches and how to leverage \pkg{EpiCompare} in the
subsections below.

@@

The first step of most data analysis is cleaning up the data
\textcolor{violet}{so it can \sout{to}} be explored. There are multiple
ways to collect the epidemiological data. Sometimes individual records
\textcolor{violet}{are collected}, with times of different states of the
epidemic (infection, recovery, etc.) as well as individual information
like network structure, location, and sub-population
information\textcolor{violet}{.\sout{will be collected, whereas}}
\textcolor{violet}{O}ther data collections will focus on aggregate
counts of individuals in each epidemic state. In fact, usually only the
number of new infections at each time step is observed and the
compartment totals
\textcolor{violet}{(amounts of individuals in each state)} are then
imputed from that along with other information about the disease and the
population of interest. \textcolor{violet}{In \pkg{EpiCompare}, w}e
focus on understanding the overall impact of an outbreak at the
aggregate/population level,
\textcolor{violet}{which allows examination of overall trends of an epidemic more easily}.

@@

\textcolor{violet}{[Ben says: this whole paragraph is new]} In order to
help the practitioner to a point in which they can examine their
epidemics from an aggregate/ population lens, we provide a function
called \texttt{agents\_to\_aggregate}. This function transforms data
that contains information about individual/agents' initial entry into
each state (e.g.~start of infection, start of recovery, etc) to an
aggregate view of how many individuals where in a state at a given time.
There are often situations where grouping agents into subpopulations
(e.g.~subpopulations defined by age or sex) can highlight different
aggregate level trends. Papers like
\citet{rvachev1985,anderson1992,worby2015} also develop state-based
models that account for subpopulations in their
models\footnote{\textcolor{violet}{[Ben says: I don't really like this sentence, but I'm trying to include the references - are they needed?]}}.
This function allows the user to easily group agents into new
subpopulations by using the \pkg{tidyverse} paradigm to first
\texttt{group\_by()}\footnote{The \texttt{group\_by} function is from
  the \pkg{dplyr} package.} the subpopulation defining features and then
aggregate (using \texttt{agents\_to\_aggregate}) conditional on these
subpopulations.

\textcolor{violet}{[Ben says: this whole paragraph is new]} The
\texttt{agents\_to\_aggregate} function is also flexible to deal with a
wide range of information about each individual. It can account for
infinitely many states, allowing the practioner to aggregate information
relative to the standard ``Suspectible'', ``Infectious'', and
``Recovered'' states (CITE) or also add states like ``Exposed'',
``iMmune'', ``Hospitalized'' and more. Additionally,
\texttt{agents\_to\_aggregate} also permits indicators for death/exit
and birth/entry dates (that change the overall number of individuals in
the population). This function is the highest tested function in this
package, and can deal with many nuances that might come-about in the
individual data. For these reasons, we view
\texttt{agents\_to\_aggregate()} as powerful tool in the step of
pre-processing data, one that quickly and simply transforms individual
level information into an aggregate view that can be processed and
analyzed in a simpler manner.

@@

\textcolor{violet}{[Ben says: this is actually an older version:]} With
raw data, getting to know our data now-a-days very frequently means
figuring out good combinations of visualizations, numerical summaries
and subsetting. An expert coder can start from
\texttt{agents\_to\_aggregate} to successfully do this in many ways, but
we've also developed tools to rapidly explore your data if your have a 3
unique states models (like the SIR model). Our \texttt{geom\_aggregate}
provides a rapid way to explore different subpopulations experience of
the epidemic, and combines the ideas behind agents\_to\_aggregate for
the SIR case, with \texttt{geom\_path} and \texttt{coord\_term} to
visualize any number of groups epidemic trajectory in 3d simplex space
using \texttt{ggplot2} and \texttt{ggtern}
\citep{Wickham2016, Hamilton2018}. Visualization tools for SIR models
were developed because (1) SIR models are some of the most common and
basic epidemic state-based models and (2) our simplex representation of
these epidemics emphasizes a ``time-invarance'' representation of the
data (for a refresher see Section \ref{sec:time-invariant}).

@@

Although this package does not focus on estimating a model for the data,
we do provide some flexible functions for simulation of basic
discrete-time epidemic-state models with Bernoulli/Multinomial
transitions which can be used to (noisily) approximate ODEs which
describe transitions from one state to the next\footnote{The original
  sentence seemed clearer to me (it may even be a run-on sentence now).
  I'm wondering if you didn't like the original sentence relative to the
  ``truth-ful-ness'' of the statement? Here's the original sentence
  slightly edited: ``Although this package does not focus on estimating
  a model for the data, we do provide some power functions for
  simulation of basic state models with Bernoulli approximation of ODE
  state models encoded in simulate\_agents and simulate\_SIR\_agents''.}.
These functions can be naturally combined with
\texttt{agents\_to\_aggregate()} to proceed in the pipeline. The
function \texttt{simulate\_SIR\_agents()} simulates an SIR epidemic with
user inputs for the number of simulations, the initial number in each
state, the infection and recovery parameters \((\beta, \gamma\)), and
the total number of discrete time steps. This function allows for easy
access to SIR model analysis and comparison. Beyond SIR models, the
function \texttt{simulate\_agents()} takes as input a user-specified
transition matrix and other epidemic parameters to allow the user to
create simulations of an outbreak for \textit{any} number of states and
any number of transitions among them. This allows for users to explore
the space of models in an intuitive way without getting bogged down by
too much mathematical detail. For consistency, we have made output from
\texttt{simulate\_agents()} and \texttt{simulate\_SIR\_agents()}
compatible with \texttt{agents\_to\_aggregate()} so aggregate
information may easily be accessed.

@@

Post-processing of modeling and simulation consists of making summary
statistics, plots, tables, and other ways to disseminate information to
the public. For example, comma separated value files (\texttt{.csv}) are
a standard way to share information within tables. However, model output
is often far more complicated than what a traditional \texttt{.csv}
would allow. As a result, a number of epidemic modeling packages return
a special class, specific to their modeling. The special classes often
contain a plethora of information from residuals, model diagnostics,
input parameters, and more. While incredibly useful, these special
classes can be difficult for novice coders to navigate.

>>>>

In this section, we present the tools implemented in \pkg{EpiCompare}
and explain how they aid in the data analysis pipeline. In Fig.
\ref{fig:pipeline2}, we illustrate how our
\textcolor{violet}{\sout{package fits} package's functions fit} into the
data analysis pipeline introduced in Fig. \ref{fig:pipeline}. All
front-facing functions are aimed to be as user-friendly as possible. We
also focus on providing the user ``tidyverse'' style functions, that
encourage piping and also follow clear verb naming schemes
\citep{Wickham2019}. Although users can typically incorporate
\pkg{EpiCompare} into any step in the data analysis process, there are
two primary points of entry. The first point of entry is the very
beginning with pre-processing and visualizing raw data, and the second
point of entry is after modeling and simulation. Figure
\ref{fig:pipeline2} captures these different paths, and we will
highlight both approaches and how to leverage \pkg{EpiCompare} in the
subsections below.

@@

The first step of most data analysis is cleaning the data
\textcolor{violet}{so it can \sout{to}} be explored. There are multiple
ways to collect epidemiological data. Sometimes individual records
\textcolor{violet}{are collected}, with times of different states of the
epidemic (infection, recovery, etc.) as well as individual information
like network structure, location, and sub-population
information\textcolor{violet}{.\sout{will be collected, whereas}}
\textcolor{violet}{O}ther data collections focus on aggregate counts of
individuals in each epidemic state. In fact, usually only the number of
new infections at each time step (e.g.~weekly case counts) is observed.
Compartment totals
\textcolor{violet}{(amounts of individuals in each state)} are then
imputed from those case counts along with other information about the
disease and the population of interest.
\textcolor{violet}{In \pkg{EpiCompare}, w}e focus on understanding the
overall impact of an outbreak at the aggregate/population level,
\textcolor{violet}{which allows examination of overall trends of an epidemic more easily}.

@@

\textcolor{violet}{[Ben says: this whole paragraph is new]} In order to
help the practitioner examine epidemics from an aggregate/ population
lens, we provide a function called \texttt{agents\_to\_aggregate}. This
function transforms data about individual/agents' initial entry into
each state (e.g.~start of infection, start of recovery, etc) to an
aggregate view of how many individuals where in a state at a given time.
There are often situations where grouping agents into subpopulations
(e.g.~subpopulations defined by age or sex) can highlight different
aggregate level trends. For example, research by
\citet{rvachev1985,anderson1992,worby2015} develop state-based models
that account for subpopulations in their
models\footnote{\textcolor{violet}{[Ben says: I don't really like this sentence, but I'm trying to include the references - are they needed?]}}.
This function allows the user to easily group agents into new
subpopulations by using the \pkg{tidyverse} paradigm to first
\texttt{group\_by()}\footnote{The \texttt{group\_by} function is from
  the \pkg{dplyr} package.} the subpopulation defining features and then
aggregate (using \texttt{agents\_to\_aggregate}) conditional on these
subpopulations.
\textcolor{orange}{I think these last two sentences are repetitive}

\textcolor{violet}{[Ben says: this whole paragraph is new]} The
\texttt{agents\_to\_aggregate} function is also flexible to deal with a
wide range of information about each individual. It can, theoretically,
account for infinitely many states, allowing the practitioner to
aggregate information relative to the standard ``Suspectible'',
``Infectious'', and ``Recovered'' states (CITE) or also add states like
``Exposed'', ``iMmune'', ``Hospitalized'' and more. Additionally,
\texttt{agents\_to\_aggregate} also permits indicators for death/exit
and birth/entry dates (that change the overall population size).
\textcolor{orange}{Don't think this is necessary \sout{This function is the highest tested function in this package, and can deal with many nuances that might come-about in the individual data.}}
The function \texttt{agents\_to\_aggregate()} is a powerful tool in the
step of pre-processing data, one that quickly and simply transforms
individual level information into an aggregate view that can be
processed and analyzed in a simpler manner.

@@

\textcolor{violet}{[Ben says: this is actually an older version:]} With
raw data, ``getting to know'' our data currently means figuring out good
combinations of visualizations, numerical summaries and subsets. An
expert coder can start from \texttt{agents\_to\_aggregate} to
successfully do this in many ways, but \pkg{EpiCompare} also includes
tools to rapidly explore your data if your has at least three epidemic
states (although these tools work best with exactly three epidemic
states). Our \texttt{geom\_aggregate} provides a rapid way to explore
different subpopulations' experience of the epidemic, and combines the
ideas behind \texttt{agents\_to\_aggregate} for the SIR case, with
\texttt{geom\_path} and \texttt{coord\_tern} to visualize any number of
groups epidemic trajectory in 3d simplex space using \pkg{ggplot2} and
\pkg{ggtern} \citep{Wickham2016, Hamilton2018}. Visualization tools for
SIR models were developed because (1) SIR models are some of the most
common and basic epidemic state-based models and (2) our simplex
representation of these epidemics emphasizes a ``time-invarance''
representation of the data (for a refresher see Section
\ref{sec:time-invariant}).

@@

Although this package does not focus on fitting a model to data, we do
provide some flexible functions for simulation of basic discrete-time
epidemic-state
models.\sout{ with Bernoulli or Multinomial transitions which can be used to (noisily) approximate ODEs which describe transitions from one state to the next}\footnote{The
  original sentence seemed clearer to me (it may even be a run-on
  sentence now). I'm wondering if you didn't like the original sentence
  relative to the ``truth-ful-ness'' of the statement? Here's the
  original sentence slightly edited: ``Although this package does not
  focus on estimating a model for the data, we do provide some power
  functions for simulation of basic state models with Bernoulli
  approximation of ODE state models encoded in simulate\_agents and
  simulate\_SIR\_agents''.}. These functions can be naturally combined
with \texttt{agents\_to\_aggregate()} to proceed in the pipeline. The
function \texttt{simulate\_SIR\_agents()} simulates an SIR epidemic with
user inputs for the number of simulations, the initial number in each
state, the infection and recovery parameters \((\beta, \gamma\)), and
the total number of discrete time steps. This function allows for easy
access to SIR model analysis and comparison. Beyond SIR models, the
function \texttt{simulate\_agents()} takes as input a user-specified
transition matrix and other epidemic parameters to allow the user to
create simulations of an outbreak for \textit{any} number of states and
any number of transitions among them. This allows for users to explore
the space of models in an intuitive way without getting bogged down by
too much mathematical detail. For consistency, we have made output from
\texttt{simulate\_agents()} and \texttt{simulate\_SIR\_agents()}
compatible with \texttt{agents\_to\_aggregate()} so aggregate
information may easily be accessed.

@@

Post-processing of modeling and simulation consists of making summary
statistics, plots, tables, and other ways to disseminate information to
the public. For example, comma separated value files (\texttt{.csv}) are
a standard way to share information within tables. However, model output
is often far more complicated than what a traditional \texttt{.csv}
would allow. \textcolor{orange}{Do we need three sentences about csvs?}
As a result, a number of epidemic modeling packages return a special
class, specific to their modeling. The special classes often contain a
plethora of information from residuals, model diagnostics, input
parameters, and more. While incredibly useful, these special classes can
be difficult for novice coders to navigate.
